Modelling and Analysis of an Elevator System with NuSMV2

### 2013-06-07 paper/main.tex
Final spellchecking.

	In this elaboration of the exercise on NuSMV2 for the Radboud University Nijmegen course ``Analysis of Embedded Systems'' we enumerate our notes and solutions for each problem. Besides this elaboration we have submitted the generated models and templates for these models by e-mail. For problem 4 and 5 we've written an application that measures the execution time for a specific model in NuSMV. The sources for this application, this report and the models can be found on Github at \url{http://github.com/Wassasin/elevatormodel}.

@@

	A user starts at a random floor and his goal is also a random floor. By uncommenting \texttt{wants\_to = user\_at \& state = idle : 0..3;}, it is possible to let a user behave in such a way that he continuously wants to go to a new floor. Otherwise, a user remains in the \texttt{idle} state when his goal has been achieved.

@@

	For this analysis we wrote a tool that generates a model for a specific number of floor and users, and measures the execution time of that model in NuSMV2. If the model checker runs for more than 2 minutes, the attempt is terminated. Below we enumerate the execution time in seconds for each instance of a model.

	Note that this tool also measures the time needed to fork it's process and to start and handle the termination of the NuSMV-process and that the execution of the NuSMV2-process may be pre-empted by the Operating System. Also note that each configuration is only tested once. Thus for models that do not need a lot of time to check (about 100 milliseconds or less), these measurements are not very accurate.

@@

		\caption{Computation time without \texttt{wants\_to}-feature}
	\end{figure}

@@

		\caption{Computation time with \texttt{wants\_to}-feature}
	\end{figure}

@@

	Thus for the realistic model, with 2 users only 3 floors can be checked within 2 minutes. For the simple model, the elevator with more than 100 floors can be checked in the same time. The \texttt{simple\_smart} model can be checked for 30 floors.

@@

	To illustrate this, we have repeated the measurements we've one for Problem 4, but with the \texttt{-t} option on an empty file. We have summarized the results below:

@@

		\caption{Computation time using \texttt{-t} on empty file without \texttt{wants\_to}-feature}
	\end{figure}

@@

		\caption{Computation time using \texttt{-t} on empty file with \texttt{wants\_to}-feature}
	\end{figure}

@@

	The following properties have all successfully been verified.

>>>>

	In this elaboration of the exercise on NuSMV2 for the Radboud University Nijmegen course ``Analysis of Embedded Systems'', we enumerate our notes and solutions for each problem. Besides this elaboration we have submitted the generated models and templates for these models by e-mail. For problem four and five we have written an application that measures the execution time for a specific model in NuSMV. The sources for this application, this report and the models can be found on Github at \url{http://github.com/Wassasin/elevatormodel}.

@@

	A user starts at a random floor and his goal is also a random floor. By uncommenting \texttt{wants\_to = user\_at \& state = idle : 0..3;}, it is possible to let a user behave in such a way that he continuously wants to go to a new floor. From now on, we refer to this as the \texttt{wants\_to} feature. Otherwise, a user remains in the \texttt{idle} state when his goal has been achieved.

@@

	For this analysis we wrote a tool that generates a model for a specific number of floors and users, and measures the execution time of NuSMV2 verifying all properties above for the generated model. If the model checker runs for more than two minutes, the attempt is terminated. Below we enumerate the execution time in seconds for each instance of a model.

	Note that this tool also measures the time needed to fork its process and to start and handle the termination of the NuSMV-process and that the execution of the NuSMV2-process may be pre-empted by the operating system. Also note that each configuration is only tested once. Thus for models that do not need a lot of time to check (about 100 milliseconds or less), these measurements are not very accurate.

@@

		\caption{Computation time without \texttt{wants\_to} feature}
	\end{figure}

@@

		\caption{Computation time with \texttt{wants\_to} feature}
	\end{figure}

@@

	Thus for the realistic model, only two users and three floors can be verified within three minutes. For the simple model, the elevator with more than 100 floors can be checked in the same time. The \texttt{simple\_smart} model can be checked for 30 floors.

@@

	To illustrate this, we have repeated the measurements we have done for Problem 4, but with the \texttt{-t} option on an empty file. We have summarized the results below:

@@

		\caption{Computation time using \texttt{-t} on empty file without \texttt{wants\_to} feature}
	\end{figure}

@@

		\caption{Computation time using \texttt{-t} on empty file with \texttt{wants\_to} feature}
	\end{figure}

@@

	The following properties have all successfully been verified in our models.
